A comprehensive analysis of natural sequence variation within the <i>Arabidopsis

### 2018-07-03 manuscript/manuscript.Rmd
echo = FALSE

```{r setup}
knitr::opts_chunk$set(warning = FALSE, collapse = TRUE, comment = "#>", tidy = TRUE, cache = TRUE, cache.lazy = FALSE, out.width = "90%", fig.height=4, fig.width=7, out.extra='style="margin: auto; display: block; padding-top: 15px;"')

>>>>

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE, collapse = TRUE, comment = "#>", tidy = TRUE, cache = TRUE, cache.lazy = FALSE, out.width = "90%", fig.height=4, fig.width=7, out.extra='style="margin: auto; display: block; padding-top: 15px;"')
